A semantics of core AUTOSAR

### 2016-08-30 paper/paper.tex
Paper: allowed pagebreaks in equation groups in the appendix
Paper: minor fix + formatting of urls in bibliography

\documentclass[10pt,conference]{IEEEtran}
%\documentclass[twocolumn]{article}
\usepackage{verbatim}
\usepackage[utf8x]{inputenc}
\usepackage[a4paper,margin=1.4cm]{geometry}
\usepackage[fleqn]{amsmath}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage[makeroom]{cancel}
\usepackage{graphicx}
\usepackage{authblk}

@@

Another line of work is obviously to lift more of the scope limitations listed in Section~\ref{sec:Lim}. A formalization of omitted component, port and event types is likely to present very few problems besides an inevitable size increase, which could be mitigated by a compartmentalization of the semantics into independent fragments. More serious work may be required to incorporate the COM layer and the added set of behaviors that follow from component distribution, but the effort would also lead to a significantly better formal coverage of the AUTOSAR specification.

The formal semantics may also provide a foundation for tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior selection of a particular platform, or translation into a low level representation. A further avenue of exploration concerns the potential of proving properties of AUTOSAR system on basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers, and in fact produced Appendix~\ref{sec:Rules} through a simple formatting translation of this file \cite{AR.eprover}.

@@

\subsection{Parallel composition}
{
\renewcommand{\Prule}[2]{#1 \quad \Pif\; #2\\}
\renewcommand{\Tstep}[3]{#1 \red{#2} #3}
\renewcommand\Pcomma{\;\text{and}\;}

\subsection{Inter-runnable variables}
\begin{eqnarray}      \InterrunnableVariables  \notag \end{eqnarray}

\subsection{Exclusive areas}
\begin{eqnarray}      \ExclusiveAreas          \notag \end{eqnarray}

\subsection{Unbuffered sending/receiving}
\begin{eqnarray}      \ReadingWriting          \notag \end{eqnarray}

\subsection{Buffered sending/receiving}
\begin{eqnarray}      \SendingReceiving        \notag \end{eqnarray}

@@

\begin{eqnarray}      \CallServer              \notag \end{eqnarray}

\renewcommand\Pcomma{\nonumber \\&&\text{and}\;\;}

\subsection{Passing back a server result}
\begin{eqnarray}      \ServerResult            \notag \end{eqnarray}

\subsection{Spawning and terminating}
\begin{eqnarray}      \SpawnTerminate          \notag \end{eqnarray}

\subsection{Passing time}
\begin{eqnarray}      \PassingTime             \notag \end{eqnarray}

%\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
\subsection{Ignoring broadcasts}
\begin{eqnarray}      \IgnoreBroadcast         \notag \end{eqnarray}

>>>>

\documentclass[10pt,conference]{IEEEtran}
\usepackage{hyperref}
%\documentclass[twocolumn]{article}
\usepackage{verbatim}
\usepackage[utf8x]{inputenc}
\usepackage[a4paper,margin=1.4cm]{geometry}
\usepackage[fleqn]{amsmath}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage[makeroom]{cancel}
\usepackage{graphicx}
\usepackage{authblk}

@@

Another line of work is to lift more of the scope limitations listed in Section~\ref{sec:Lim}. A formalization of omitted component, port and event types is likely to present very few problems besides an inevitable size increase, which could be mitigated by a compartmentalization of the semantics into independent fragments. More serious work may be required to incorporate the COM layer and the added set of behaviors that follow from component distribution, but the effort would also lead to a significantly better formal coverage of the AUTOSAR specification.

The formal semantics may also provide a foundation for tools that analyze or transform AUTOSAR models. One such example is our AUTOSAR simulator \cite{ARSim}, which interprets AUTOSAR models entirely on basis of the transition system, utilizing truly random scheduling and a maximum progress assumption to select among available transitions at each step. The benefit of this simulator is its ability to dynamically execute AUTOSAR Software Component models as they are, without prior selection of a particular platform, or translation into a low level representation. A further avenue of exploration concerns the potential of proving properties of AUTOSAR systems on the basis of their semantics. To prepare for this opportunity, we have defined the transition system used in this paper as a Horn clause file readable by common theorem provers, and, in fact, Appendix~\ref{sec:Rules} is automatically produced through a simple formatting translation of this file \cite{AR.eprover}.

@@

\subsection{Parallel composition}
{
\renewcommand{\Prule}[2]{#1 \quad &\Pif\; #2\\}
\renewcommand{\Tstep}[3]{#1 \red{#2} #3}
\renewcommand\Pcomma{\;\text{and}\;}

\begin{align}  \CombRed  \notag \end{align}
}

\subsection{Inter-runnable variables}
\begin{align}      \InterrunnableVariables  \notag \end{align}

\subsection{Exclusive areas}
\begin{align}      \ExclusiveAreas          \notag \end{align}

\subsection{Unbuffered sending/receiving}
\begin{align}      \ReadingWriting          \notag \end{align}

\subsection{Buffered sending/receiving}
\begin{align}      \SendingReceiving        \notag \end{align}

@@

\begin{align}      \CallServer              \notag \end{align}

\renewcommand\Pcomma{\nonumber \\&\text{and}\;\;}

\subsection{Passing back a server result}
\begin{align}      \ServerResult            \notag \end{align}

\subsection{Spawning and terminating}
\begin{align}      \SpawnTerminate          \notag \end{align}

\subsection{Passing time}
\begin{align}      \PassingTime             \notag \end{align}

%\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
%**TODO: check page-break
\newpage
\subsection{Ignoring broadcasts}
\begin{align}      \IgnoreBroadcast         \notag \end{align}
